\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-11 paper.tex

\subsubsection{Broker}
Brokers represent data providers and consumers to do computing tasks in the DLT (Distributed Ledger Technology) since brokers are expected to have high computing power. Once a data provider wants to launch a new product, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel. For each products, brokerage fees will be charged by the broker.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{system_design}
    \caption{System Design.}
    \label{fig:system_design}
\end{figure}

@@

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys. Only one Registration Contract is needed, and everyone can query the participants' public keys. Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications. After that, their identities are available in the Registration Contract and launching and trading processes can be started.

\subsection{Launching and Searching Products}

To sell the streaming data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract. Each product has a Product Contract to record the participants, subscription price brokerage fee, quantity of data and  trading process.

Brokers certify session keys as well. Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers. However, it is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss. Therefore, Blind signature is used to prevent the situation. Figure \ref{fig:key_certification} shows the certification process. When a data provider asks a broker to ceritfy new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded. Then the data provider sends the blinded session key $Blind(k)$ to the broker. The broker signs the message and returns the signature $Sign(Blind(k))$ to data provider. The data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.

>>>>

\subsubsection{Broker}
Brokers represent data providers and consumers to do computing tasks since brokers are expected to have higher resource. Some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Once a qualified data provider requests to launch a new product, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel. For each product, brokerage fees will be charged by the broker.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{system_design}
    \caption{The system design of a decentralized architecture which consist of a registrar, data providers, consumers and brokers.}
    \label{fig:system_design}
\end{figure}

@@

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID documents and public keys. Everyone can query participants' public keys. Those who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications. After that, their identities are available in the Registration Contract and launching and trading processes can be started.

\subsection{Launching and Searching Products}
To sell the streaming data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract. Each product has a Product Contract to record the participants, subscription price brokerage fee, quantity of data and  trading process.

Brokers certify session keys as well. Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers. Figure \ref{fig:key_certification} shows the certification process. When a data provider asks a broker to ceritfy new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded. Then the data provider sends the blinded session key $Blind(k)$ to the broker. The broker signs the message and returns the signature $Sign(Blind(k))$ to data provider. The data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.
